---
title: "Lynsey Keator Assignment #10"
date: "April 21 2020"
author: "Lynsey Keator"
output: html_notebook
---

## 1. Write a script to import and tidy the Johnson Elementary Project Data.

```{r}

# Load packages
library(tidyverse)
library(here)

# Read in data
data <-read_csv(here("Data", "Johnson Elementary ELA Project.csv"),
                skip = 4,
                col_names = c("Room", 
                              "ID", 
                              "Tardies/Absences", 
                              "Q1", 
                              "Q2", 
                              "Q3", 
                              "Q4"),
                col_types = cols(Room = col_factor()))

# Fill missing room labels and separate Tardies,Absences into 2 columns using pipe

data <- data %>%
  fill(Room) %>%
  separate('Tardies/Absences', into = c("Tardies", "Absences"), sep =";")

data$Tardies <- parse_double(data$Tardies)

data$Absences <- parse_double(data$Absences)
typeof(data$Tardies)
typeof(data$Absences)

```


## 2. Write a script to provide summary statistics for the number of tardies and absences for each room.


```{r}

summarystatistics <- data %>%
  group_by(Room) %>%
  summarize(Tardies_mean = mean(Tardies),
            Tardies_SD = sd(Tardies),
            Absences_mean = mean(Absences),
            Absences_sd = sd(Absences))
                              
summarystatistics

```

## 3. Write a script to show the frequency of missing data points for each quarter by room.

```{r}

missingdata <- data%>%
  group_by(Room) %>%
  count(sum(is.na(Q1:Q4)))

```


## 4. Construct a graph that illustrates the median rating trends across the four quarters for the fifth-grade classes.

```{r}

```

## 5. Use the NYC flights data to construct a graph that compares carriers in terms of the proportion of 2013 flights that arrived on time when traveling from NYC to ATL. Your graph should include a title and easy-to-read labels, including the names of airlines rather than airline codes.

```{r}
# Load the data
flights <-read_csv(here("Data", "NYC Flights 2013.csv"))

# Graph carriers in terms of proportion of 2013 flights on time from NYC to ATL

nyflights <- flights %>%
  filter(origin %in% c("JFK", "LGA"), dest == "ATL") 

# sum = 256

otflights <- flights %>%
  filter(arr_delay == 0, origin %in% c("JFK", "LGA"), dest == "ATL") 

# arr_delay == 0 sum = 256

nyflights$prop <- sum(nyflights$arr_delay)
nyflights$prop

  ggplot(aes(nyflights, x = carrier, y = arr_delay)) +
  geom_point() +
  labs(title = "On Time Arrivals from NYC to ATL",
       x = "Carrier",
       y = "Proportion of 2013 On Time Arrivals")

```

