---
title: "Lynsey Keator Assignment #10"
date: "April 21 2020"
author: "Lynsey Keator"
output: html_notebook
---

## 1. Write a script to import and tidy the Johnson Elementary Project Data.

```{r echo=TRUE}

# Load packages
library(tidyverse)
library(here)

# Read in data
data <-read_csv(here("Data", "Johnson Elementary ELA Project.csv"),
                skip = 4,
                col_names = c("Room", 
                              "ID", 
                              "Tardies/Absences", 
                              "Q1", 
                              "Q2", 
                              "Q3", 
                              "Q4"),
                col_types = cols(Room = col_factor()))

# Fill missing room labels and separate Tardies,Absences into 2 columns using pipe

data <- data %>%
  fill(Room) %>%
  filter(!is.na(ID)) %>%
  separate('Tardies/Absences', into = c("Tardies", "Absences"), sep =";")

# Read tardy and absense columns as doubles, not characters
data$Tardies <- parse_double(data$Tardies)
data$Absences <- parse_double(data$Absences)
```

## 2. Write a script to provide summary statistics for the number of tardies and absences for each room.


```{r echo=TRUE}

summarystatistics <- data %>%
  group_by(Room) %>%
  summarize(Tardies_mean = mean(Tardies, na.rm = TRUE),
            Tardies_SD = sd(Tardies, na.rm = TRUE),
            Absences_mean = mean(Absences, na.rm = TRUE),
            Absences_sd = sd(Absences, na.rm = TRUE))
                              
summarystatistics

```

## 3. Write a script to show the frequency of missing data points for each quarter by room.
```{r include=FALSE}
data.long <- data %>%
  gather(Q1:Q4, key = "Quarter", value = "Rating")

data.long
```

```{r echo=FALSE}

missing.data <- data.long %>%
  group_by(Room, Quarter) %>%
  summarize(sum(is.na(Rating)))

missing.data
```

## 4. Construct a graph that illustrates the median rating trends across the four quarters for the fifth-grade classes.

```{r echo=FALSE}

data.long %>%
  group_by(Room, Quarter) %>%
  summarize(median_qscores = median(Rating, na.rm = TRUE)) %>%
  ggplot(aes(x = Quarter, y = median_qscores, group = Room)) +
  geom_line(aes(color = Room)) +
  facet_wrap(vars(Room)) +
  guides(color = "none") +
  labs(x = "Quarter", 
       y = "Median ELA Ratings",
       title = "Fifth Grade ELA Ratings")

```

## 5. Use the NYC flights data to construct a graph that compares carriers in terms of the proportion of 2013 flights that arrived on time when traveling from NYC to ATL. Your graph should include a title and easy-to-read labels, including the names of airlines rather than airline codes.
```{r include=FALSE}
# Load the data

flights <-read_csv(here("Data", "NYC Flights 2013.csv"))
```

```{r echo=FALSE}
flights %>%
  mutate(on_time = (arr_delay <= 0)) %>%
  filter(dest == "ATL", !is.na(on_time)) %>%
  ggplot(aes(x = carrier)) + 
  geom_bar(aes(fill = on_time), position = "fill") +
  labs(title = "2013 On-Time Arrivals: NYC -> ATL",
       x = "Carrier",
       y = "Proportion Flights (On-Time : Delayed)") +
  scale_fill_discrete(name = "Status",
                      labels = c("Not on Time", "On Time")) +
  scale_x_discrete(labels = c("Endeavor Air",
                              "Delta",
                              "ExpressJet",
                              "AirTran",
                              "Envoy",
                              "United",
                              "Southwest"))
```
